Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-11-01 analysis/paper/paper.qmd
combined gis maps

# data only for LGM period
tcsa_lgm <- korean_archaeological_site_locations_tcsa %>% 
  filter(age< 26.5 & age> 19)

# ggmap(map)  +
#   geom_jitter(data = tcsa_lgm,
#              aes(long_dd.y ,
#                  lat_dd.y,
#                  colour = min_tcsa),
#              size = 3,
#              width = 0.25, 
#              height = 0.25) +
#   scale_color_viridis_c(option = "A") +
#   theme_minimal(base_size = 6) +
#   labs(x = "Longitute",
#        y = "Latitude") +
#   theme(axis.title.x = element_blank(),
#         axis.title.y = element_blank())

library(sf)

veg <- read_sf(here("analysis/data/gis_data/vegetation_polygons.shp"))

# st_crs(veg)

veg <- st_transform(veg, crs = st_crs(4162))

# take a look
ggplot() +
  geom_sf(data = veg) +
  coord_sf()

# BM: basic plan is the do a spatial join with the veg zones and the TCSA values. Then table of artefacts will get a new column telling us what veg zone it is in. Then we can make a plot to compare the distribution of tcsa values across the different veg zones

# Determine which points fall inside which polygons

# Convert to class 'sf'
pts <- st_as_sf(tcsa_lgm,
                coords = c(   "long_dd.y", "lat_dd.y"),
                crs = st_crs(veg))

# take a look
ggplot() +
  geom_sf(data = pts)

points_in_veg_zones <- 
st_join(veg, 
        pts, 
        join = st_contains)

ggplot() +
  geom_sf(data = veg, aes(fill = veg$Vegetation)) + #add color for vegetation polygons
  geom_sf(data = pts, aes(color = pts$min_tcsa)) +
  theme_minimal()

# fill=c("#CCCCCC", "#FFFFFF", "#999999", "#666666")

ggplot(points_in_veg_zones) +
  aes(Vegetation,
      min_tcsa) +
  geom_boxplot() +
  geom_quasirandom()

summary(aov(min_tcsa ~ as.factor(Vegetation), points_in_veg_zones))

@@

ggplot() +
  geom_sf(data = veg_all) +
  coord_sf()

pts_all <- st_as_sf(korean_archaeological_site_locations_tcsa,
                coords = c("long_dd.y", "lat_dd.y"),
                crs = st_crs(veg_all))
ggplot() +
  geom_sf(data = pts_all)

@@

ggplot() +
  geom_sf(data = veg_all, aes(fill = veg_all$ecoregion)) + #add color for vegetation polygons
  geom_sf(data = pts_all, aes(color = pts_all$min_tcsa)) +
  theme_minimal()

ggplot(points_in_veg_zones_all) +
  aes(ecoregion,
      min_tcsa) +
  geom_boxplot() +
  geom_quasirandom()

@@

ggplot() +
  geom_sf(data = veg_forest) +
  coord_sf()

pts_forest <- st_as_sf(korean_archaeological_site_locations_tcsa,
                coords = c("long_dd.y", "lat_dd.y"),
                crs = st_crs(veg_forest))
ggplot() +
  geom_sf(data = pts_forest)

@@

ggplot() +
  geom_sf(data = veg_forest, aes(fill = Zone)) + #add color for vegetation polygons
  geom_sf(data = pts_forest,size = 3, aes(color = min_tcsa)) +
  theme_minimal()

@@

ggplot(points_in_veg_zones_forest_box) +
  aes(Zone,
      min_tcsa) +
  geom_boxplot() +
  geom_quasirandom()

@@

>>>>

@@

# ggplot() +
#   geom_sf(data = veg_all) +
#   coord_sf()

pts_all <- st_as_sf(korean_archaeological_site_locations_tcsa,
                coords = c("long_dd.y", "lat_dd.y"),
                crs = st_crs(veg_all))
# ggplot() +
#   geom_sf(data = pts_all)

@@

eco_plot <- ggplot() +
  geom_sf(data = veg_all, aes(fill = "grey")) +
   geom_sf_text(data = veg_all, aes(label = ecoregion), size =3.5)+
  geom_sf(data = pts_all, aes(color = min_tcsa)) +
  theme_minimal() +
  scale_fill_brewer(palette="Greys") +
  labs(color="TCSA") +
  guides(fill = FALSE) +
  theme(axis.text.x = element_text(size = 6))+
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank())

eco_box <- ggplot(points_in_veg_zones_all) +
  aes(ecoregion,
      min_tcsa) +
  geom_boxplot() +
  geom_quasirandom() +
  xlab("Vegetation") + 
  ylab("TCSA")

@@

# ggplot() +
#   geom_sf(data = veg_forest) +
#   coord_sf()

pts_forest <- st_as_sf(korean_archaeological_site_locations_tcsa,
                coords = c("long_dd.y", "lat_dd.y"),
                crs = st_crs(veg_forest))
# ggplot() +
#   geom_sf(data = pts_forest)

@@

for_plot <- ggplot() +
  geom_sf(data = veg_forest, aes(fill = "grey")) +
  geom_sf_text(data = veg_forest, aes(label = Zone), size =3.5)+
  geom_sf(data = pts_forest,size = 3, aes(color = min_tcsa)) +
  theme_minimal()+
  scale_fill_brewer(palette="Greys") +
  labs(color="TCSA") +
  guides(fill = FALSE) +
  theme(axis.text.x = element_text(size = 6)) +
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank())

@@

for_box <- ggplot(points_in_veg_zones_forest_box) +
  aes(Zone,
      min_tcsa) +
  geom_boxplot() +
  geom_quasirandom() +
  xlab("Ecoregion") + 
  ylab("TCSA")

@@

plot_grid(eco_plot, for_plot, eco_box, for_box, labels = c('A', 'C', 'B', 'D'))
```
